\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-30 paper/main.tex
minor updates

We employ another mechanism to avoid redundancy and fading signals in stacked graph convolutional networks, which was introduced by \citet{DeepGCN2019} and refined in \citet{DeeperGCN2020}. The authors propose a residual network architecture and normalization scheme, solving these issues in a variety of graph predicting tasks. This structure is depicted in Figure~\ref{fig:ResGraphConvBlocks} resulting in reusable residual blocks, which can be stacked multiple times, thereby not losing focus of each node neighbourhood. \\

\subsubsection{Hyperparameter tuning}
To find the best hyperparameter configuration for the proposed model we performed a grid search, to find the most expressive and non-redundant representation. Therefor, we pretrained the bottom-up and the top-down model separately and aimed at best performing models w.r.t. previously described metrics. Embedding sizes, depth of the neural network, optimizer, learning rate and layer types were found from an extensive, manual grid search.

>>>>

We employ another mechanism to avoid redundancy and fading signals in
stacked graph convolutional networks, which was introduced by
\citet{DeepGCN2019} and refined in \citet{DeeperGCN2020}. The authors
propose a residual network architecture and normalization scheme. This
structure is depicted in Figure~\ref{fig:ResGraphConvBlocks} resulting
in reusable residual blocks, which can be stacked multiple times,
thereby not losing focus of each node neighbourhood.

\subsubsection{Hyperparameter tuning}
To find the best hyperparameter configuration for the proposed model
we performed a grid search to find the most expressive and
non-redundant representation. We pretrained the bottom-up and the
top-down model separately and aimed at best performing models
w.r.t. previously described metrics. We optimized embedding sizes,
depth of the neural network, optimizer, learning rate and layer types
using an extensive, manual grid search. \todo[inline]{Specify range of
  values searched here; even better if you have the intermediate
  results and can put them here (better: in the supplement).}
